Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2016-12-22 ms_pre_post.Rmd
Add three references of note to cite later
Edits to second paragraph of Discussion; progress on 'degeneracy' in the third

For example, our results highlight a simple but theoretically under-developed conclusion concerning the relationship between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance. Post-copulatory inbreeding avoidance is useless for monandrous females, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably. In contrast, pre-copulatory inbreeding avoidance is perhaps most effective for monandrous females and less effective for polyandrous females. This conclusion is reflected in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D). The effect of monandry on selection for pre-copulatory inbreeding avoidance was weaker, but pre-copulatory inbreeding avoidance was generally stronger when populations where monandrous (e.g., Figure 3A vs 3B; see also Supporting Information p. S1-1). In addition to polyandry increasing selection for post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1). It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry. To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandrous and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.

Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, realised through functionally different traits. Pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability. Hence, evolution of each of these strategies might make the other strategy more or less adaptive by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression.

<!--- Some general conclusions addressing 1) what future theory should be developed, and 2) what future empirical studies need to consider. For 2, need to be aware of both pre- and post-copulatory inbreeding avoidance, potentially, and that the two are not independent, necessarily; cannot find any general theory for what happens when you have this kind of strategy redundancy -- two ways of getting at the same outcome. --->

>>>>

For example, our results highlight a fundamental but theoretically under-developed conclusion concerning the relationship between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance. Post-copulatory inbreeding avoidance is useless for monandrous females, and most effective for highly polyandrous females that can choose amongst multiple mates to ensure that offspring are fertilised favourably. In contrast, pre-copulatory mechanisms are most salient for monandrous females that have no post-copulatory means for avoiding inbreeding. This conclusion is reflected in our simulation results, as selection for post-copulatory inbreeding avoidance was negligible in monandrous populations, resulting in high drift of allele values over generations due to the inability of females to express post-copulatory choice (e.g., Figure 4C,D). The effect of monandry on selection for pre-copulatory inbreeding avoidance was weaker, but pre-copulatory inbreeding avoidance was generally stronger when populations where monandrous (e.g., Figure 3A vs 3B; see also Supporting Information p. S1-1). In addition to polyandry increasing selection for post-copulatory inbreeding avoidance, polyandry might also covary positively with post-copulatory inbreeding avoidance due to the feed back that post-copulatory inbreeding avoidance has on facilitating evolution of polyandry itself, as observed in our model (Figure 1). It would therefore be interesting to test the hypothesis that, across taxa, occurrence of post-copulatory inbreeding avoidance covaries positively, and pre-copulatory inbreeding avoidance covaries negatively, with degree of polyandry. To test this hypothesis, more work is needed to identify the degree to which females of different species engage in polyandry and the degree to which females express both pre-copulatory and post-copulatory inbreeding avoidance.

Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits. Pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability. Hence, evolution of each of these strategies might make the other strategy more or less adaptive by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression. The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].

<!--- Some general conclusions addressing 1) what future theory should be developed, and 2) what future empirical studies need to consider. For 2, need to be aware of both pre- and post-copulatory inbreeding avoidance, potentially, and that the two are not independent, necessarily; cannot find any general theory for what happens when you have this kind of strategy redundancy -- two ways of getting at the same outcome. See: @Nowak1997, @Edelman2001, @Whitacre2010, @Price2002, @Park2013, Atamas2009, @Whitacre2012, @Whitacre2010a, @Levin2008 --->
